Boundary Labeling for annotated documents

### 2018-03-24 LaTeX/Paper.tex
Paper: Wrote Section 3.4, edited chapter 3. Program: No changes.

\section{Architecture}
 Most of the calculations are done side-by-side with the visualization, as the position of each word is both used in the creation of the routing graph and when displaying the final result. The routing itself is done separately from this process in its own class, as the finished routing graph suffices here. This allows for different  routing algorithms to be implemented separately. %Since we only want to create leaders that don't intersect with the text, the graph was created alongside the placement of the words on the canvas.%, as it was easy to extract measurements at this point. Due to some problems with Java's various methods of calculating linebreaks, this process was done completely by hand.
\section{GUI}

The GUI of the program is very simplistic, as the main goal was to demonstrate the routing algorithm. As such, all customization options are located on the control panel above the drawing area, which contains the text, leaders and annotations. (See also Fig.~\ref{fig:ProgWindow})

The control panel's first three options determine the font the program uses, whether it is bold or italicized and its size. The fourth and last option allows the selection of different routing algorithms. After changing any value, the program will automatically redraw the drawing area's contents, and re-do the routing.

The drawing area itself can't be interacted with, it only serves to display the algorithm's results.
\begin{figure}
	\captionsetup{justification=centering, margin=0.75cm}
	\centering
	\includegraphics[scale=0.75]{ProgramWindowAnnotated.png}
	\caption{<test>}
	\label{fig:ProgWindow}
\end{figure}

@@

Displaying the text on-screen without losing the position of the whitespace characters turned out to be harder than expected. While Java offers a class that divides any string of characters in separate lines, the resulting object doesn't allow for the line's text to be extracted again, which makes it unusable for our purposes. This problem was solved by placing each word manually on the screen. For simplicity's sake, we only allowed line breaks between words.

Another issue was the visualization of the routing graph and the leaders. While JGraphT offers ways to display graphs, it wasn't possible to influence the placement of individual nodes. Our solution was forgoing these options and drawing the graph manually, assigning coordinates to each vertex when created. Vertices are represented by small rectangles, whereas edges are represented with straight lines. To avoid confusion between crossing leaders and leaders that incorporate the same vertex in their path, but curve away from each other, all leaders are drawn with rounded edges.

@@

%As the Graph's vertices represent fixed locations on the canvas, they each have coordinates associated with them, with the vertices representing the sites containing extra information, such as references to the corresponding annotation and to the leader connecting the two (if existent).
%The additional information stored in the vertices is used for both routing and drawing the leaders: The routing was done via a depth-first search algorithm that prioritized vertices located further up if possible, and vertices to the right otherwise. After the algorithm terminates, it returns  a vertex-based graph walk describing the route from the site to the border of the text area alongside information about where to draw the OPO-segment in the buffer zone if successful, or a walk containing only the starting vertex, if no valid path was found. Using this information alongside the positional data stored in the vertices, the polyline representing the leader can be drawn.

>>>>

\section{Architecture}
The program is divided into three parts. The GUI and program window only propagate user interaction to other parts of the program. It will be discussed further in the next section.
The main drawing area handles the visualization of the results, calculates where to place the text on-screen, and also generates the routing graph, as this can be done alongside the text placement.
The routing is done in a separate class, and can easily be switched out for another algorithm because of this.
%The routing itself is handled separately from this process in its own class, as the finished routing graph suffices here. This facilitates the implementation of additional routing algorithms and allows for easy switching. The only other notable part of the program is the GUI, which will be discussed in the next section.%Since we only want to create leaders that don't intersect with the text, the graph was created alongside the placement of the words on the canvas.%, as it was easy to extract measurements at this point. Due to some problems with Java's various methods of calculating linebreaks, this process was done completely by hand.
\section{GUI}
\label{sec:GUI}

The GUI of the program is kept simple, as the main goal was to demonstrate the routing algorithm. All customization options are located on the control panel above the drawing area, which contains the text, leaders and annotations. (See also Fig.~\ref{fig:ProgWindow})

The control panel's first three options determine the font the program uses, whether it is bold or italicized and its size. The fourth and last option allows the selection of different routing algorithms. After changing any value, the program will automatically be notified of the changes and react accordingly.

The drawing area itself can't be interacted with, it only serves to display the algorithm's results.
\begin{figure}
	\captionsetup{justification=centering, margin=0.75cm}
	\centering
	\includegraphics[scale=0.75]{ProgramWindowAnnotated.png}
	\caption{Picture of the routing program}
	\label{fig:ProgWindow}
\end{figure}

@@

Displaying the text on-screen without losing the position of the whitespace characters turned out to be harder than expected. While Java offers a class that divides any string of characters in separate lines, the resulting line object doesn't allow for it's text to be extracted, which makes it unusable for our purposes. This problem was solved by placing each word manually on the screen. For simplicity's sake, we only allowed line breaks between words, whenever a whitespace character was encountered.

Another issue was the visualization of the routing graph and the leaders. While JGraphT offers ways to display graphs, it wasn't possible to influence the placement of individual vertices. Our solution was forgoing these options and drawing the graph manually, assigning coordinates to each vertex on creation. Vertices are represented by small rectangles, whereas edges are represented with straight lines. To avoid confusion between crossing leaders and leaders that incorporate the same vertex in their path, but curve away from each other, all leaders are drawn with rounded corners.

%Add Test data generation/retrieval here?

@@

When the program starts, it first goes through the text word by word in reading order, placing each word $w \in W$  on-screen, and saving the content of each encountered annotation for later. As the words are placed, vertices are added to the graph after each word, and at the start and end of each line. Source vertices are inserted whenever an annotation is encountered, and contain a reference to their annotation in addition to the information contained in regular vertices.

After the text has been processed, additional vertices are inserted into each line between the last word of that line and the right text border, located directly above or below vertices in the neighboring lines. Whenever a vertex is inserted exactly above or below another vertex in a neighboring line, they are immediately connected via an edge, whereas all vertices in the same space between lines $s \in S$ are connected in order of their x-coordinates after all vertices have been placed.

Once the graph has been generated, a list of all source vertices in reading order is passed to the selected routing algorithm, which then determines leader routing and annotation placement for each of them and returns the results to the main program, which then draws the results. (For details on the routing algorithm, see section~\ref{sec:AlgDesc}.)

If any of the parameters on the control panel (see section~\ref{sec:GUI}) are changed, the process re-starts from the beginning.
%As the Graph's vertices represent fixed locations on the canvas, they each have coordinates associated with them, with the vertices representing the sites containing extra information, such as references to the corresponding annotation and to the leader connecting the two (if existent).
%The additional information stored in the vertices is used for both routing and drawing the leaders: The routing was done via a depth-first search algorithm that prioritized vertices located further up if possible, and vertices to the right otherwise. After the algorithm terminates, it returns  a vertex-based graph walk describing the route from the site to the border of the text area alongside information about where to draw the OPO-segment in the buffer zone if successful, or a walk containing only the starting vertex, if no valid path was found. Using this information alongside the positional data stored in the vertices, the polyline representing the leader can be drawn.
